
\begin{abstract} % 摘要
  \LaTeX{}\footnote{\url{https://en.wikipedia.org/wiki/LaTeX}}是一种基
  于\TeX{}\footnote{\url{https://en.wikipedia.org/wiki/TeX}}文件格式的
  排版系统，由美国电脑学家莱斯利·兰伯特在20世纪80年代初期开发。利用这种
  格式，即使用户没有排版和程序设计的知识，也可以充分利用\TeX{}所提供的
  强大功能，在几天，甚至几小时内生成很多具有书籍质量的印刷品。对于生成
  复杂表格和数学公式，这一点表现得尤为突出。因此它非常适用于生成高印刷
  质量的科技和数学类文档。这个系统同样适用于生成从简单如信件到完整如书
  籍的所有种类的文档\cite{wiki:latexcn}。

  本文对如何利用\LaTeX{}来撰写西南林业大学本科毕业论文做一个简要的介绍。
  读者也可以将本文作为毕业论文模板来使用\footnote{本文所使用的毕业论文
    模板（\texttt{cls}文件），\texttt{tex}源文件，及其它相关文件都可以
    在下面的网址找到：%
    \url{https://github.com/wx672/texmf/tree/master/doc/latex/swfu/swfcthesis/tutorial}}。
\end{abstract}

\begin{keyword} % 关键词
  \LaTeX{}；西南林业大学；本科毕业论文模板；教程
\end{keyword}

\begin{EAbstract} % 英文摘要
  \LaTeX{} is a document preparation system. When writing, the writer uses plain text as
  opposed to formatted text as users of word processors like Microsoft Word. The writer
  uses markup tagging conventions to define the general structure of a document (such as
  article, book, and letter), to stylise text throughout a document (such as bold and
  italic), and to add citations and cross-references. A \TeX{} distribution such as
  \TeX{}Live or Mik\TeX{} is used to produce an output file (such as PDF or DVI) suitable
  for printing or digital distribution. Within the typesetting system, its name is
  stylised as \LaTeX{}\cite{wiki:latex}.

  This short tutorial shows you how to write an undergraduate thesis in \LaTeX{}. It can
  also serve as a perfect template to ease your thesis writing\footnote{The class file
    used for typesetting this thesis, and the \texttt{tex} source of this file can be
    found at \url{https://github.com/wx672/texmf/tree/master/doc/latex/swfu/swfcthesis}.}.
\end{EAbstract}

\begin{EKeyword} % 英文关键词
  \LaTeX{}; \TeX{}; thesis; template; SWFU
\end{EKeyword}

%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: "../tutorial"
%%% End:
