\documentclass[letter,12pt]{letter}

\usepackage{swfuletter}
\usepackage{lipsum}

\begin{document}

\begin{letter}{}
% Wang Xiaolin
% Senior Professor, 
% College of Big Data and Intelligence Engineering
% Southwest Forestry University
% Kunming 650224, Yunnan, China
% Phone:
% Email:

  \address{WANG Xiaolin (Mr.)\\
    Lecturer,\\
    Southwest Forestry University,\\
    Kunming, China\\
    Email: \emph{wx672ster@swfu.edu.cn}\\
    Phone: 86+13577067397
  }
  \signature{WANG Xiaolin\sign{signature}{seal}{0,1.5cm}}
  \date{\today}

  \opening{To whom it may concern,}

  I am delighted to recommend Junbo LUO for admission to Master's
  program in Environmental Intelligence at Macao Polytechnic
  University.  As his mentor and a lecturer at College of Big Data and
  Intelligence Engineering of Southwest Forestry University, I had the
  privilege of knowing him over four years during his undergraduate
  studies.  LUO Junbo is a standout student who exemplifies
  intellectual rigor, and I highly commend him for his analytical
  acumen and critical thinking, coupled with a disciplined approach to
  complex problem-solving, which highlights their capacity to thrive
  in demanding settings. He is a natural leader who can inspires and
  motivates others. His ability to manage projects efficiently and
  lead with clarity and purpose sets them apart.

  What truly distinguishes Junbo LUO is his professional and
  goal-oriented approach to problem-solving. He excels in building
  positive relationships and communicating effectively, making him an
  asset in any collaborative environment. These qualities, combined
  with his drive and adaptability, make me confident he will succeed
  in his future academic and professional life.  I strongly recommend
  Junbo LUO for any endeavours he wishes to undertake. I would be
  grateful this recommendation is favorably considered.

  \closing{Yours sincerely,}

\end{letter}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
